Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-06 document/ms.tex
a few notes

\begin{figure}[htbp]
\begin{center}
\subfigure[one-over-efficiency]{%
\includegraphics[width=0.45\textwidth]{figures/synthetic-vmax-radius.pdf}
}
\subfigure[fully-marginalized forward model]{%
\includegraphics[width=0.45\textwidth]{figures/synthetic-radius.pdf}
}
\end{center}
\caption{%
The inferred distribution of exoplanet radii based on a noisy observation of a
synthetic catalog.
The red dotted line shows the true distribution function and the black
histograms are the constraints from the different inference techniques.
\figlabel{synthetic-radius}}
\end{figure}

@@

It has been shown that the joint period--radius distribution for exoplanets is
not separable (\dfmtodo{CITE}).
In this section, we discuss non-separable model in our analysis framework.

We model the rate function $\rate(\period,\,\radius)$ as a piecewise constant
function in rectangular bins in $\ln\period$ and $\ln\radius$.
The parameters \ratepars\ that we're fitting are the values of each of these
bins (subject to a normalization constraint).

>>>>

% \begin{figure}[htbp]
% \begin{center}
% \subfigure[one-over-efficiency]{%
% \includegraphics[width=0.45\textwidth]{figures/synthetic-vmax-radius.pdf}
% }
% \subfigure[fully-marginalized forward model]{%
% \includegraphics[width=0.45\textwidth]{figures/synthetic-radius.pdf}
% }
% \end{center}
% \caption{%
% The inferred distribution of exoplanet radii based on a noisy observation of a
% synthetic catalog.
% The red dotted line shows the true distribution function and the black
% histograms are the constraints from the different inference techniques.
% \figlabel{synthetic-radius}}
% \end{figure}

\section{Extrapolation to Earth}

@@
